Computation and comparison of the stable Northeastern US marine boundary layer

### 2020-12-04 Paper/main.tex
More nomenclature stuff

\section{Nomenclature}
{\renewcommand\arraystretch{1.0}
  \noindent\begin{longtable*}{@{}l @{\quad=\quad} l@{}}
ABL       & Atmospheric Boundary Layer \\
$\alpha$  & Wind shear exponent  \\
$\beta$   & Thermal expansion coefficient \\
$c_p$     & Specific heat capacity \\
$\Delta, \Delta_{x,y,z}$  & Grid spacing, grid spacing in x, y, z directions \\
$f$       & Frequency \\
$f_{max}$  & Maximum resolvable frequency due to mesh limits \\
$f_{Ny}$   & Nyquist frequency \\
$g, g_i$   & Gravitational acceleration \\
$k, TKE$  & Turbulent kinetic energy \\
$L$       & Turbulent integral length scale \\
$L_{Ob}$   & Obukhov length scale \\
$\nu_t$   & Turbulent viscosity \\
LES       & Large Eddy Simulation \\
$\rho$    & Density \\
$\rho_\circ$ & Reference density  \\
$\phi_h$  & Potential temperature gradient \\
$Pr_t$    & Turbulent Prandtl number \\
$R$       & Universal gas constant \\
$R_{ij}$   & Two point correlation tensor \\
SBL       & Stable Boundary Layer \\
$\theta$  & Potential temperature \\
$S_i$     & Wind spectra \\
$\sigma_i$ & Wind speed variance \\
$\tau_{ij}$ & Shear stress \\
$TI$      & Turbulence intensity \\
$\overline{U}_{horiz}$ & Time averaged horizontal velocity \\
$u_\tau$   & Friction velocity    \\
$V_1$     & Resolved wind speed at first grid level 
\end{longtable*}}

>>>>

\section{Nomenclature}
{\renewcommand\arraystretch{1.0}
  \noindent\begin{longtable*}{@{}l @{\quad=\quad} l@{}}
ABL       & Atmospheric Boundary Layer \\
$\alpha$  & Wind shear exponent  \\
$\beta$   & Thermal expansion coefficient \\
$c_p$     & Specific heat capacity \\
$C_\epsilon$  & Turbulence model constant \\
$\Delta, \Delta_{x,y,z}$  & Grid spacing, grid spacing in x, y, z directions \\
$f$       & Frequency \\
$f_{max}$  & Maximum resolvable frequency due to mesh limits \\
$f_{Ny}$   & Nyquist frequency \\
$g, g_i$   & Gravitational acceleration \\
$h$       & Enthalpy \\
$k, TKE$  & Turbulent kinetic energy \\
$L$       & Turbulent integral length scale \\
$L_{Ob}$   & Obukhov length scale \\
$\nu_t$   & Turbulent viscosity \\
LES       & Large Eddy Simulation \\
$\rho$    & Density \\
$\rho_\circ$ & Reference density  \\
$\phi_h$  & Potential temperature gradient \\
$Pr_t$    & Turbulent Prandtl number \\
$R$       & Universal gas constant \\
$R_{ij}$   & Two point correlation tensor \\
SBL       & Stable Boundary Layer \\
$\theta$  & Potential temperature \\
$S_i$     & Wind spectra \\
$\sigma_i$ & Wind speed variance \\
$\tau_{ij}$ & Stress tensor \\
$TI$      & Turbulence intensity \\
$\overline{U}_{horiz}$ & Time averaged horizontal velocity \\
$u_\tau$   & Friction velocity    \\
$V_1$     & Resolved wind speed at first grid level 
\end{longtable*}}
